Mining Planet Search Data for Binary Stars: The $\psi^1$ Draconis system [UPDATE PLOTS!]

### 2015-09-09 paper/ms.tex
Updated paper.

%\documentclass[12pt,preprint]{aastex}
\documentclass[twocolumn]{emulateapj}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{subfigure}
\usepackage{url}
%\usepackage{algpseudocode}
\usepackage{verbatim}
\usepackage{ amssymb }
\bibliographystyle{astroads}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}
\begin{document}

@@

We used the \emph{Austral} code \citep{Endl2000} to measure the differential radial velocity of $\psi^1$ Dra A at each observation. We provide the raw velocity measurements in Table \ref{tab:rv_data}, as well as the velocities shifted into the system velocity rest frame. The velocity shift necessary to convert from the differential radial velocities to this frame is found in Section \ref{sec:orbit}. Table \ref{tab:rv_data} also gives the measurements of the companion radial velocity (described in the next section).

\begin{deluxetable}{lrrrrrr}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
%\tablenum{1}
\tablecaption{Observations of $\psi^1$ Dra A \label{tab:rv_data}}
\tablehead{
\colhead{Julian Date} & \multicolumn{3}{c}{Primary RV (m/s)} & \multicolumn{3}{c}{Secondary RV (m/s)} \\
& \colhead{raw} & \colhead{shifted} & \colhead{$\sigma$}  & \colhead{raw} & \colhead{shifted}  & \colhead{$\sigma$} }

@@

\begin{deluxetable}{lrrrrrr}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
\tablenum{1}
\tablecaption{Observations of $\psi^1$ Dra A (continued)}
\tablehead{
\colhead{Julian Date} & \multicolumn{3}{c}{Primary RV (m/s)} & \multicolumn{3}{c}{Secondary RV (m/s)} \\
& \colhead{raw} & \colhead{shifted} & \colhead{$\sigma$}  & \colhead{raw} & \colhead{shifted}  & \colhead{$\sigma$} }

@@

\section{Mass Ratio Estimation}
\label{sec:orbit}

@@

We use the emcee code \citep{emcee} to perform a Markov Chain Monte Carlo (MCMC) fit to an orbital solution. We fit the semi-amplitudes for both the primary and secondary stars (K1 and K2, respectively), the longitude of pericenter ($\omega$), the eccentricity (e), and the periastron passage epoch ($T_0$). In addition to the orbital parameters, we fit a velocity offset for both the primary and secondary star measurements ($\Delta v_1$ and $\Delta v_2$, respectively). We need to fit two velocity offsets because neither measurement is an absolute radial velocity measurement, and because they were measured in very different ways. We also fit a scale factor to apply to the uncertainties in the secondary star velocity measurements, which is necessary because the FWHM of the peak over-estimates the uncertainty in the peak velocity (see Figure \ref{fig:ccf_typical}), but should still be proportional to it (i.e. a broader peak has a higher uncertainty than a narrower peak). Finally, we account for radial velocity variations caused by instrumental or astrophysical noise by fitting an "RV jitter" term, which we add in quadrature to the primary star uncertainties. This term acts to increase the uncertainties on most other parameters, and so makes our estimates more conservative. Since the measured primary star velocities are differential and the measured secondary star velocities are measured in the rest frame of the primary star, we cannot measure the system radial velocity.

 We give the median value and uncertainty for each parameter in Table \ref{tab:orbit}. The uncertainties are estimated from the posterior probability distribution samples such that the lower and upper bounds give the 16th and 84th percentile (i.e. they are $1\sigma$ confidence intervals). We plot the best-fit orbit with the data in Figure \ref{fig:orbit}, with the uncertainties on the companion velocities scaled. We show the posterior probability distributions for the orbital parameters in Figure \ref{fig:orbit_dist} and for the data shifting and scaling parameters ($\Delta v_1$, $\Delta v_2$, and the uncertainty scaling) in Figure \ref{fig:datamanip_dist}.

>>>>

%\documentclass[12pt,preprint]{aastex}
\documentclass[twocolumn]{emulateapj}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{subfigure}
\usepackage{url}
%\usepackage{algpseudocode}
\usepackage{verbatim}
\usepackage{ amssymb }
\usepackage{amsmath}
\bibliographystyle{astroads}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}
\begin{document}

@@

We used the \emph{Austral} code \citep{Endl2000} to measure the differential radial velocity of $\psi^1$ Dra A at each observation by comparing each spectrum to a high signal-to-noise ratio template spectrum of the same star. We provide the raw velocity measurements in Table \ref{tab:rv_data}, as well as the velocities shifted into the system velocity rest frame. The velocity shift necessary to convert from the differential radial velocities to this frame is found in Section \ref{sec:orbit}. Table \ref{tab:rv_data} also gives the measurements of the companion radial velocity (described in the next section).

\begin{deluxetable}{lrrrrrr}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
%\tablenum{1}
\tablecaption{Observations of $\psi^1$ Dra A \label{tab:rv_data}}
\tablehead{
\colhead{Julian Date} & \multicolumn{3}{c}{Primary RV (km/s)} & \multicolumn{3}{c}{Secondary RV (km/s)} \\
& \colhead{raw} & \colhead{shifted} & \colhead{$\sigma$}  & \colhead{raw} & \colhead{shifted}  & \colhead{$\sigma$} }

@@

\begin{deluxetable}{lrrrrrr}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
\tablenum{1}
\tablecaption{Observations of $\psi^1$ Dra A (continued)}
\tablehead{
\colhead{Julian Date} & \multicolumn{3}{c}{Primary RV (km/s)} & \multicolumn{3}{c}{Secondary RV (km/s)} \\
& \colhead{raw} & \colhead{shifted} & \colhead{$\sigma$}  & \colhead{raw} & \colhead{shifted}  & \colhead{$\sigma$} }

@@

@@

\section{Orbital Fit}
\label{sec:orbit}

We now use the radial velocity measurements to find the best orbital parameters to describe the orbit, as well as some data scaling and shifting factors. The orbit is described by the semi-amplitudes for both the primary and secondary stars (K1 and K2, respectively), the longitude of pericenter ($\omega$), the eccentricity (e), the period ($P$), and the periastron passage epoch ($T_0$). We cannot measure the system radial velocity, which is usually the final orbital element, because the measured primary star velocities are differential and the measured secondary star velocities are measured relative to the primary star.

Since the primary star radial velocity measurements are differential measurements, we must also fit a constant shift ($\Delta v_1$) to account for the absolute radial velocity of the primary at the time in which our template spectrum was observed. We include an RV jitter term ($\sigma_J$) to the fit to account for radial velocity variations not encompassed by the orbital solution, and add the value in quadrature with the formal uncertainties on the primary star velocity measurements.

The companion radial velocities are measured relative to the primary star plus a small velocity shift ($\Delta v_2$) caused by a slight inaccuracies in the vacuum to air wavelength conversion in the model spectrum. Finally, the CCF peak full-width at half maximum vastly over-estimates the velocity uncertainty and so we fit a scale factor ($f$) to apply to the companion velocity uncertainties. The uncertainties given in Table \ref{tab:rv_data} are already scaled by this factor. The full log-likelihood function ($\mathcal{L}$) is then given by:

\begin{align*}
s_1 &= \sum_{t_m} \frac{(v_{1,m} - v_1(t_m) - \Delta v_1)^2 }{\sigma_{v_1}^2 + \sigma_J^2} + \ln{2\pi(\sigma_{v_1}^2 + \sigma_J^2)} \\
s_2 &= \sum_{t_m} \frac{(v_{2,m} - v_2(t_m)(1+\frac{K_1}{K_2}) - \Delta v_2)^2}{f\sigma_{v_2}^2 } + \ln{2\pi(f\sigma_{v_2}^2)} \\ 
\mathcal{L} &= -0.5(s_1 + s_2) \\
\end{align*}

where $v_{1,2}(t) = v(T_0, P, e, K_{1,2}, \omega, t)$ is the velocity at time t given by the orbital elements $T_0, P, e, K$, and $\omega$.

We use the affine invariant sampler provided in the emcee code \citep{emcee} to perform a Markov Chain Monte Carlo (MCMC) fit to all of the parameters described above. We use flat priors in all variables except for the RV jitter and companion rv uncertainty scale factors ($\sigma_J$ and $f$, respectively), for which we use log-uniform priors to allow for a large range of values.  We give the median value and uncertainty for each parameter in Table \ref{tab:orbit}. The uncertainties are estimated from the posterior probability distribution samples such that the lower and upper bounds give the 16th and 84th percentile (i.e. they are $1\sigma$ credibility intervals). We plot the best-fit orbit with the data in Figure \ref{fig:orbit}, with the uncertainties on the companion velocities scaled and the velocities shifted by $\Delta v_1$ and $\Delta v_2$. We show the posterior probability distributions for the orbital parameters in Figure \ref{fig:orbit_dist} and for the data shifting and scaling parameters ($\Delta v_1$, $\Delta v_2$, and the uncertainty scaling) in Figure \ref{fig:datamanip_dist}.
